Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-22 Docs/TODAES/paper.tex
update files
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} \label{tab:Description-of-Benchmarks} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\end{tabular}\par
\bigskip
\end{minipage}

>>>>

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{TheMathWorks2013}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}
